\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Large \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-9pt}
\begin{center}
	{\Large \scshape {David E. Hale}}\\
	New York City, NY $\cdot$ \href{mailto:Hale.David.Edward@gmail.com}{Hale.David.Edward@gmail.com} $\cdot$ (203)-460-2168 $\cdot$ \href{http://linkedin.com/in/david-hale-2598a791/}{LinkedIn Link}\\
\end{center}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}
\textbf{Oscar Health Insurance} \hfill New York City, NY\\
\textit{Operations Analyst (Level 3), Process Design and Tech Strategy} \hfill August 2021 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt

    \item   Charged with developing new workflows, deciding what can/should be automated, writing and handing off technical requirements to engineering team. 

    \item   Responsible for creating, standardizing, automating, and maintaining new workflows for claims proccessing in accordance with both optimizational efficiency improvments, and 
	\item 	I take a workflow, break it down into its constituent parts, analyze how to improve it, and either personally automate the parts that can be automated, or project manage the engineering team in the development of the new automation, and train processors on any remaining manual parts, and create end-to-end documentation.
	\item 	Responsible for designing, automating, and implementations of new workflows for adjudicating health insurance claims, as well as training insurance claims processors in new workflows.
	\item 	In response to Medicare audits, found source of mis-adjudicated claims in tech stack, fixed automations, and retrained processors in correct workflow.
	\item 	Automated analyses resulting in freeing up $\approx{6}$ person team for other analysis.
	\item 	Hand picked for SWAT team working on company wide claims adjudication issues.
	\item 	Identified \$3.8 Million dollars in overpayments and \textasciitilde{}120,000 claims paid out incorrectly from misconfigured automations and implemented fixes to allow for recoupment.
\end{itemize}

\textbf{MTA, Transit Adjudication Bureau} \hfill New York City, NY\\
\textit{Data/System Analyst (Consultant)} \hfill November 2020 - August 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Project Manager charged with overseeing all coordination and triaging of MTA IT Projects for all updates to proprietary MTA IT systems.
            Responsiblities included identifying requirements, defining acceptance criteria, performing QA UAT, creating documentation for, and performing user trainings on the new software updates.
	% \item Coordinated all communication and projects with MTA IT for the Transit Adjudication Bureau. Supplied first level solutions where possible, documented, and provided escalation for serious issues.
    %\item Data extraction expert. Generated all reports, KPI's, and adhoc analyses used for deciding public policy with outside organizations including NYC City Hall and and the NYPD.
    % \item Business Analyst for workflow improvement/proprietary software improvements. Responsible for creating documentation and writing up system improvements.
	% \item Conducted QA tests and approval for software improvements before introduction to production environment.
	\item Designed, built, and produced weekly, monthly, and annual reports using SQL and Microsoft PowerBI.
\end{itemize}

\textbf{Alternative Transportation Systems, LLC.} \hfill Boston, MA\\
\textit{Business Analyst} \hfill June 2019 - November 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed and built business automation processes including payroll, employee recertification and testing, and scripted KPI report generation resulting in $\sim$10\% reduction of manual office workload. 
    Created, modularized, and modernized, a system of scripts into a source controlled library to serve these automations using Python, ODBC, SQL, JavaScript, and Google Apps Script.
	\item Designed and deployed an app using Google Apps Script and AppSheet and integrated with Atlassian API to trigger, triage, and track vehicle maintenance and repair work. This app processes over 1,600 data points/day from 50+ users/day, resulting in faster data flow, expediting preventative maintenance actions by up to a month.
	\item Designed and built a live profitability tracker used by c-suite management to measure operational efficiency, income, and profit margins using SQL, Google Apps Script, Google Maps API, and Google Sheets.
	\item Automated invoice generation in a scalable trackable, and maintainable practice using a Google Sheets interface, allowing nontechnical staff to configure over 30 different rate types across 80+ contracts in a centralized cloud-based solution, completely replacing the manual billing calculation workflows.
	% \item Created and deployed a full-stack ecosystem linking a SQL database to Google Suite using R in a FIPPs and HIPAA compliant manner. This system displays live geographic information and driver shifts used to manage 50+ routes at once.
    % \item Generated all KPI’s such as On-Time Performance, trips per hour, etc. as needed by management, including demand sensing, capacity measurements and predictive modeling.
	% \item Presided over IT provisioning, technical support, and training for over 60 users.
	% \item Oversaw contractual rate negotiations, work acceptance or rejection, and operations for a \$90,000/month contract.
\end{itemize}



\header{Skills}
\begin{tabular}{ l l }
	Programming:    &   Python, R, JavaScript, Google Apps Script, SQL, BigQuery, Git, Clasp, REST API\\
    Processes:      &   Issue Triaging, Project Management, UAT \& QA, Automation, Documentation,\\ 
                    &   User Trainings, Troubleshooting,  Data Analytics
\end{tabular}
\vspace{2mm}


\header{Awards}
\textbf{Oscar Hackathon Q3 2022} \hfill August 2022\\
Won first place in Operations Excellence for React App using Regex to identify types of medical codes. 
\vspace*{2mm}

\ 
\end{document}